coDoc: A Tool for Managing Relationships between Driver code and Documents

### 2013-02-12 P4-5-page-paper/paper.tex
backup

\title{Checking Inconsistency between Driver code and Document}
\author{Dejun Qian\\Department of Computer Science\\Portland State University\\Portland, OR 97201\\dejun@pdx.edu}

@@

\begin{abstract}
This report presents how we implement coDoc. 
Experiment result shows that, with our effert in this project, coDoc can provide forthfold, 
1) provide the ability to display code and document. 
2) select code based on syntax parsing.
3) make relationship between code and document.
4) analyze relationship.
\end{abstract}

>>>>

\title{coDoc: A Tool for Managing Relationships between Driver code and Documents}
\author{Dejun Qian\\Department of Computer Science\\Portland State University\\Portland, OR 97201\\dejun@pdx.edu}

@@

\begin{abstract}
When writing software, 
we need the documents in hand, 
especially when we are developing driver software.
This paper presents how we implement coDoc. 
Experiment result shows that, with our effert in this project, coDoc can provide forthfold, 
1) provide the ability to display code and document. 
2) select code based on syntax parsing.
3) make relationship between code and document.
4) analyze relationship.
\end{abstract}
